Ornaments as indicators of social changes and cultural practices in northeastern Taiwan before and after European colonial period

### 2019-12-11 analysis/paper/paper.Rmd
adjust the heading in the table and edit the figure caption

```{r C14-data, fig.cap= "Summed probability distributions for dates from Kiwulan. The dark line represents the summed probabilities of all radiocarbon ages, and the grey lines in the background are the probabilities of individual ages. Grey rectangles indicate the approximate chronology of the major archaeological components of the deposit. Ages calibrated with the Bchron package (Parnell et al. 2008). "}

@@

```{r C14-table-data}
table_kw_dates <-
  kw_dates %>% 
  mutate(`Depth related to sea level (cm)` = paste0(Depth1, " to ", Depth2)) %>% 
  mutate(`Pit-Layer` = paste0(Square, "-", Layer)) %>% 
  left_join(kw_age_cali_df_tidy, "Pit-Layer") %>% 
  mutate(ave = (`2.5%` + `97.5%`) / 2) %>% 
  mutate(ave = ifelse(is.na(ave), 200, ave)) %>%  
  arrange(ave) %>% 
  dplyr::select("Period", "Pit-Layer", "Depth related to sea level (cm)", "Date BP", "Calibrated date (95% conf. level)", "Details") %>% 
  mutate(`Calibrated date (95% conf. level)` = 
           ifelse(is.na(`Calibrated date (95% conf. level)`), "-", `Calibrated date (95% conf. level)`))

>>>>

```{r C14-data, fig.cap= "Summed probability distributions for dates from Kiwulan. The dark line represents the summed probabilities of all radiocarbon ages, and the grey lines in the background are the probabilities of individual ages. Grey rectangles indicate the approximate chronology of the major archaeological components of the deposit. For the upper component, the blue line indicates the start of European presence, while the red line is the Chinese presence. Ages calibrated with the Bchron package (Parnell et al. 2008). "}

@@

```{r C14-table-data}
table_kw_dates <-
  kw_dates %>% 
  mutate(`Above mean sea level (cm)` = paste0(Depth1, " to ", Depth2)) %>% 
  mutate(`Pit-Layer` = paste0(Square, "-", Layer)) %>% 
  left_join(kw_age_cali_df_tidy, "Pit-Layer") %>% 
  mutate(ave = (`2.5%` + `97.5%`) / 2) %>% 
  mutate(ave = ifelse(is.na(ave), 200, ave)) %>%  
  arrange(ave) %>% 
  dplyr::select("Pit-Layer", "Above mean sea level (cm)", "Date BP", "Calibrated date (95% conf. level)", "Details") %>% 
  mutate(`Calibrated date (95% conf. level)` = 
           ifelse(is.na(`Calibrated date (95% conf. level)`), "—", `Calibrated date (95% conf. level)`))
